\documentclass{beamer}
\title{Assignment 1: Tools}
%\subtitle{}
\author{$<$Name of Business Manager$>$}
\subject{Tools}
\usetheme{Darmstadt}
\usecolortheme{beaver}
\useoutertheme{infolines}
\useinnertheme{circles}

\setbeamertemplate{footline} { 
  \leavevmode
  \hbox{\begin{beamercolorbox}[wd=.5\paperwidth, ht=2.5ex, dp=1.125ex,
        leftskip=.3cm, rightskip=.3cm plus1fill]{author in head/foot}
      \usebeamerfont{author in head/foot}\insertshortdate
  \end{beamercolorbox}
  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.5ex, dp=1.125ex, 
        leftskip=.3cm plus1fill, rightskip=.3cm]{title in head/foot}
    \usebeamerfont{title in head/foot}\insertshortauthor
  \end{beamercolorbox}}
  \vskip0pt
}

\begin{document}
\maketitle
\frame{
  \transdissolve[duration=0.25]
  \frametitle{The Team}
  \framesubtitle{Ryan Alcoran, Joe Lee, Shivalik Narad, Nam Phan, Swapna Vemparala, Amber Wong}
  \begin{center}
    {\Huge Team Q 06}\\[1em]
  \end{center}
  \pause
  \begin{itemize}
    \item Alcoran, Ryan \{unspecified\}
      \pause
    \item Lee, Joe \{Project Manager, Business Manager\}
      \pause
    \item Narad, Shivalik \{unspecified\}
      \pause
    \item Phan, Nam \{Development Manager, Test Manager\}
      \pause
    \item Vemparala, Swapna \{Project Manager, Risk Manager, Business Manager\}
    \pause
    \item Wong, Amber \{unspecified\}
  \end{itemize}
}

\frame{
  \transdissolve[duration=0.25]
  \frametitle{Software Configuration Management (SCM)}
  \framesubtitle{Tracking and controlling changes in software}
  \begin{center}
    {\Huge Git} \\[1em]
    \pause
    License: GNU General Public License (GPL) v2\\[2em]
    \pause
    \begin{itemize}
      \item Command line git client can be used.
        \pause
      \item Graphical git client can be used.
        \pause
      \item Can be integrated into IDEs like Eclipse, using a plug-in.
    \end{itemize}
  \end{center}
}

\frame{
  \transdissolve[duration=0.25]
  \frametitle{Software hosting facilities}
  \begin{center}
    {\Huge GitHub} \\[1em]
    \pause
    Public code hosting.
  \end{center}
}

\frame{
  \transdissolve[duration=0.25]
  \frametitle{Standalone bug trackers}
  \begin{center}
    {\Huge Bugzilla} \\[1em]
    \pause
    License: Mozilla Public License (MPL)
  \end{center}
  \pause
  \begin{itemize}
    \item Track bugs and code changes.
      \pause
    \item Communicate with teammates.
      \pause
    \item Submit and review patches.
      \pause
    \item Manage quality assurance (QA).
  \end{itemize}
}

\frame{
  \transdissolve[duration=0.25]
  \frametitle{Editors and IDEs}
  \pause
  \begin{center}
  \begin{itemize}
    \item {\bf Eclipse}
      \pause
      \begin{itemize}
        \item License: MPL
          \pause
        \item IDE framework
          \pause
        \item Tools framework\\[1em]
      \end{itemize}
      \pause
    \item {\bf GNU Emacs}
      \pause
      \begin{itemize}
        \item License: GNU GPLv3
          \pause
        \item Text editor
          \pause
        \item Extensible
          \pause
        \item Customizable
      \end{itemize}
  \end{itemize}
  \end{center}
}

\frame{
  \transdissolve[duration=0.25]
  \frametitle{Project Management Tools}
  \begin{center}
    {\Huge OpenProj}\\[1em]
    \pause
    Common Public Attribution License (CPAL) 1.0\\[2em]
    \pause
    {\Huge Agilefant \pause (maybe?)}\\[1em]
    \pause
    Expat (MIT) License
  \end{center}
}

\end{document}
